MaxEnt: What is it good for?

### 2015-06-18 ms.tex
Words around entropy formula
Testable information that's equivalent to conditioning

Relative entropy
\begin{eqnarray}
H(p; q) &=& -\sum_i p_i \log\left(\frac{p_i}{q_i}\right) 
\end{eqnarray}

@@

\section{A special case: updating given propositions}

>>>>

The relative entropy of distribution $p$ from distribution $q$ is:
\begin{eqnarray}
H(p; q) &=& -\sum_i p_i \log\left(\frac{p_i}{q_i}\right) 
\end{eqnarray}
and we are to choose the distribution $p$ to maximise $H$ subject to the
constraints of normalisation and any other constraints.

@@

\section{A special case: updating given propositions}
Consider the following testable information:

\begin{eqnarray}
P(D) = 1
\end{eqnarray}
where $D$ is a proposition about the value of $x$. For example, consider
updating from the prior $q(x)$ shown in Figure~\ref{fig:distribution}, to
a posterior $p(x)$, using the testable information
\begin{eqnarray}
P(3 \leq x \leq 5) = 1.
\end{eqnarray}
